NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PE and PG lipids

### 2019-04-17 Manuscript/manuscriptPGPE.tex
Add calcium density profiles

\todo{There are mass density profiles available from CHARMM simulations, preliminary figures should be made:
http://nmrlipids.blogspot.com/2017/03/nmrlipids-iv-headgroup-glycerol.html?showComment=1501446779291#c7311317114567929503}

>>>>

\begin{figure}[]
  \centering
  \includegraphics[width=8.0cm]{../Figs/CAdensPG.eps}
  \caption{\label{CAdensPG}
    Calcium ion density profiles along membrane normal
    from different simulations with PG lipids.
  }
\end{figure}
